\documentclass[12pt, notitlepage]{article}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\geometry{a4paper}                   		% ... or a4paper or a5paper or ... 
%\geometry{landscape}                		% Activate for rotated page geometry
\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
								% TeX will automatically convert eps --> pdf in pdflatex

\usepackage{hyperref}
		
%SetFonts

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

\usepackage{tgbonum}

%SetFonts

\title{
	\textbf{
		Introductory Questionnaire
	} \\
	\large{Plant Physiological Ecology} \\
	\large{Spring 2023}
}

\date{\vspace{-5ex}}

\def\wl{\par \vspace{\baselineskip}}

\begin{document}

{\fontfamily{phv}\selectfont %select helvetica (code = phv)

\maketitle

\Large{\textbf{Name:} \underline{\hspace{10cm}}}

\section{What is your academic level?}
\begin{itemize}
	\item{\underline{\hspace{1cm}} PhD}
	\item{\underline{\hspace{1cm}} MS}
	\item{\underline{\hspace{1cm}} Undergraduate Senior}
	\item{\underline{\hspace{1cm}} Undergraduate Junior}
	\item{\underline{\hspace{1cm}} Undergraduate Sophomore}
	\item{\underline{\hspace{1cm}} Undergraduate Freshman}
	\item{\underline{\hspace{1cm}} Other (please specify)}
\end{itemize}

\section{Have you ever taken a collegiate course that has covered or been focused in 
Ecology? If so, what was the name, number, and level of the course (e.g., lower-level Undergraduate,
upper-level Undergraduate, Graduate)?}

\wl
\wl
\wl
\wl
\wl
\wl
\wl
\wl

\section{Have you ever taken a collegiate course that has covered or been focused in 
Plant Physiology? If so, what was the name, number, and level of the course 
(e.g., lower-level Undergraduate, upper-level Undergraduate, Graduate)?}

\newpage

\section{Have your ever (please mark all that apply):}
\begin{itemize}
	\item{grown a plant \underline{\hspace{1cm}}}
	\item{grown a garden \underline{\hspace{1cm}}}
	\item{read a scientific article \underline{\hspace{1cm}}}
	\item{searched for a scientific article \underline{\hspace{1cm}}}
	\item{performed a scientific experiment \underline{\hspace{1cm}}}
	\item{performed a scientific experiment involving plants \underline{\hspace{1cm}}}
	\item{analyzed data \underline{\hspace{1cm}}}
	\item{disseminated scientific findings \underline{\hspace{1cm}}}
	\item{written code (of any sort) \underline{\hspace{1cm}}}
	\item{used Web of Science \underline{\hspace{1cm}}}
	\item{used Google Scholar \underline{\hspace{1cm}}}
	\item{used BlackBoard \underline{\hspace{1cm}}}
	\item{used Git \underline{\hspace{1cm}}}
	\item{used R \underline{\hspace{1cm}}}
\end{itemize}

\newpage

\section{What do you hope to achieve by taking this class? 
Be as vague or specific as you'd like.}

\wl
\wl
\wl
\wl
\wl
\wl
\wl
\wl
\wl
\wl
\wl
\wl

\section{Do you have any concerns you'd like me to know about?}

} %end font selection

\end{document}

